Modelling BCG vaccination in the UK

### 2019-07-30 rmds/06-tb-bcg-improv-outcomes.Rmd
started importing fitting results

```{r setup, include = FALSE, eval = TRUE}
## Word count: 3869
## Packages
library(tidyverse)
library(knitr)
library(kableExtra)
library(pander)
library(prettypublisher)

>>>>

```{r 06-setup, include = FALSE, eval = TRUE}
## Word count: 3869
## Packages
library(tidyverse)
library(knitr)
library(kableExtra)
library(pander)
library(prettypublisher)

### 2019-07-30 rmds/09-model-fitting.Rmd
started importing fitting results

## Wordcount: 5501
##packages
library(tidyverse)
library(kableExtra)
library(pander)
## Resources path
resources_path <- file.path("chapters", "model_fitting")

## Read data: https://github.com/seabbs/ModelTBBCGEngland/data
load_formated <- function(name) {

  path <- file.path("chapters/model-development/data", paste0(name, ".rda"))

  load(path, envir = globalenv())
}

load_formated("measurement_params_table")
```

@@

7. SMC-SMC model fitting with 2000 initial parameter particles. Particle rejuvernation was set to trigger when the effective sample size decreased below 25%, with 5 MCMC steps used each time.

@@

As discussed, there were multiple issues with fitting the final model and this made it diffult to determine what the mean of posterior distribution was. This made manually tuning the proposal distribution challenging and so instead a standard deviation of 10% was used. This value was chosen as it increased the acceptance rate by limiting each rejuvernation step to a relatively small subset of the prior distribution whilst not preventing the exploration of new parameter space in scenarios when model fits from the initial particle sample were poor.

@@

* Compare Scenarios using DIC and discuss results.
* Table of DIC results with scenarios

@@

* Plot of TB data and fit
* Table of data and fit
* Comment on fit

### Model fit to TB age distribution

* Age group plot over time + fit
* Age distribution over time + fit
* Comment on fit

@@

* Plot of Posterior Parameter distributions
* Table of Posterior Parameter distributions
* Comment on posteriors

>>>>

## Wordcount: 5501
##packages
library(tidyverse)
library(purrr)
library(kableExtra)
library(pander)
library(fs)
## Resources path
resources_path <- file.path("chapters", "model-fitting")

## Path to plots
plots_path <- file.path(resources_path, "plots")

## Read data: https://github.com/seabbs/ModelTBBCGEngland/data
load("chapters/model-development/data/measurement_params_table.rda")

## Read in model fits from https://github.com/seabbs/vignettes/results/final-fit
files <- fs::dir_ls("chapters/model-fitting/data")

load_rds <- function(file) {
  name <- basename(file) %>%
    stringr::str_replace("\\.rds", "")

  assign(name, readRDS(file), envir = globalenv())
}

walk(files, load_rds)

## Load Scenario DICs
load_rds("chapters/model-fitting/scenario_dics.rds")

## Function to handle variable names
replace_code_with_form <- function(param) {
  param %>%
    str_replace("beta_young_adult", "$\\\\beta_{\\\\text{young adult}}$") %>%
    str_replace("M_young_adult", "$M_{\\\\text{young adult}}$") %>% 
    str_replace("M", "$M$") %>%
    str_replace("\\$M\\$_", "M_") %>% 
    str_replace("meas_error", "$E_{\\\\text{syst}}$") %>% 
    str_replace("meas_std", "$E_{\\\\text{noise}}$") %>% 
    str_replace("c_eff", "$c_{\\\\text{eff}}$") %>% 
    str_replace("c_hist_half", "$c^{\\\\text{hist}}_{\\\\text{half}}$") %>% 
    str_replace("c_hist", "$c^{\\\\text{hist}}_{\\\\text{eff}}$") %>% 
    str_replace("non_uk_scaling", "$\\\\iota_{\\\\text{scale}}$") %>% 
    str_replace("older_adult_activation_scaling", "$\\\\epsilon^{\\\\text{older-adult}}_L$")
}
```

@@

7. SMC-SMC model fitting with 2000 initial parameter particles. Particle rejuvernation was set to trigger when the effective sample size decreased below 25%, with 10 MCMC steps used each time.

@@

As discussed, there were multiple issues with fitting the final model and this made it diffult to determine what the mean of posterior distribution was. This made manually tuning the proposal distribution challenging and so instead a standard deviation of 2.5% was used. This value was chosen as it increased the acceptance rate by limiting each rejuvernation step to a relatively small subset of the prior distribution whilst not preventing the exploration of new parameter space in scenarios when model fits from the initial particle sample were poor.

@@

* Compare Scenarios using DIC and discuss results.

```{r 09-scenarios-table, eval = FALSE}
tibble(Scenario = names(scenario_dics) %>% str_split("_") %>% 
         map_chr(~paste(., collapse = " ")), 
       DIC = unlist(transpose(scenario_dics)$dic)) %>% 
  arrange(DIC) %>% 
  mutate(Scenario = Scenario %>% 
           str_replace("plus", "and") %>% 
           str_replace("baseline", "Baseline") %>% 
           str_replace("transmission", "Transmission variable in young adults (15-29)") %>% 
           str_replace("mixing", "non-UK born mixing variable in young adults (15-29)") %>% 
  str_to_sentence()) %>% 
kable(
  caption = "DIC values for each scenario evaluated during model fitting - arranged from best to worst model fit.", booktabs = TRUE, longtable = TRUE) %>% 
  kable_styling(latex_options = c("hold_position"))
```

@@

* Comment on fit

```{r 09-table-incidence-preds, eval = FALSE}
sum_obs_table %>% 
  set_names(., nm = c(names(.)[-ncol(.)], "Predicted Incidence (95% CI)*")) %>% 
kable(
  caption.short = "Observerd versus predicted overall TB incidence for years that the model was fitted too.", 
  caption = "Observerd versus predicted overall TB incidence for years that the model was fitted too. The model underpredicted incidence for all years fitted too. The upper credible interval of the model predictions was substantially lower than the observed data. ", booktabs = TRUE, longtable = TRUE) %>% 
  kable_styling(latex_options = c("hold_position")) %>% 
  add_footnote(label = "* 95% credible interval estimated using the 2.5% quantile and the 97.5% quantile.", notation = "none")
```

```{r 09-age-strat-incidence, fig.scap = "Observed and predicted TB incidence stratified by model age group", fig.cap = "Observed and predicted TB incidence stratified by model age group (0-11). 0-9 refers to 5 year age groups from 0-4 years old to 45-49 years old. 10 refers to those aged between 50 and 69 and 11 refers to those aged 70+. The model underpredicted incidence in all age groups fitted too with older adults have the best fit."}
knitr::include_graphics(file.path(plots_path, "overview-states-1990-age-1.png"))
```

@@

* Comment on posteriors

```{r 09-format-variables-names}
params <- sum_prior_posterior$Parameter %>% 
  replace_code_with_form()

legend_params <- map2_chr(sum_prior_posterior$Parameter, 
                          params,
                          ~ paste(.x, .y,  sep = " - ")) %>% 
  paste0(collapse = ", ")
```

```{r 09-fig-prior-params, fig.scap = "Prior and posterior distributions for fitted model parameters.", fig.cap = paste0("Prior and posterior distributions for fitted model parameters. Parameter names in figure are in their coded form. They can be interpreted using the following: ", legend_params)}
knitr::include_graphics(file.path(plots_path, "prior-posterior-overview-1.png"))
```

```{r 09-prior-posterior}
sum_prior_posterior %>% 
  set_names(., nm = . %>% 
              str_replace("or", "or (95%CI)\\*\\*")) %>%
  mutate(Parameter = Parameter %>% 
           replace_code_with_form()) %>%
kable(
  caption.short = "Observerd versus predicted overall TB incidence for years that the model was fitted too.", 
  caption = "Observerd versus predicted overall TB incidence for years that the model was fitted too. The model underpredicted incidence for all years fitted too. The upper credible interval of the model predictions was substantially lower than the observed data. ",
  booktabs = TRUE, longtable = TRUE, escape = TRUE) %>% 
  kable_styling(latex_options = c("hold_position")) %>% 
  add_footnote(label = c("* 95% credible interval estimated using the 2.5% quantile and the 97.5% quantile."),
                        notation = "none")
```

### 2019-07-30 rmds/10-model-results.Rmd
started importing fitting results

##packages
library(tidyverse)
library(kableExtra)
library(pander)
## Resources path
resources_path <- file.path("chapters", "model_results")
```

@@

>>>>

##packages
library(tidyverse)
library(purrr)
library(kableExtra)
library(pander)
library(fs)

## Resources path
resources_path <- file.path("chapters", "model-fitting")

## Path to plots
plots_path <- file.path(resources_path, "plots")

## Read in model fits from https://github.com/seabbs/vignettes/results/final-fit
files <- fs::dir_ls("chapters/model-fitting/data")

load_rds <- function(file) {
  name <- basename(file) %>%
    stringr::str_replace("\\.rds", "")

  assign(name, readRDS(file), envir = globalenv())
}

walk(files, load_rds)

## Function to handle variable names
replace_code_with_form <- function(param) {
  param %>%
    str_replace("beta_young_adult", "$\\\\beta_{\\\\text{young adult}}$") %>%
    str_replace("M_young_adult", "$M_{\\\\text{young adult}}$") %>% 
    str_replace("M", "$M$") %>%
    str_replace("\\$M\\$_", "M_") %>% 
    str_replace("meas_error", "$E_{\\\\text{syst}}$") %>% 
    str_replace("meas_std", "$E_{\\\\text{noise}}$") %>% 
    str_replace("c_eff", "$c_{\\\\text{eff}}$") %>% 
    str_replace("c_hist_half", "$c^{\\\\text{hist}}_{\\\\text{half}}$") %>% 
    str_replace("c_hist", "$c^{\\\\text{hist}}_{\\\\text{eff}}$") %>% 
    str_replace("non_uk_scaling", "$\\\\iota_{\\\\text{scale}}$") %>% 
    str_replace("older_adult_activation_scaling", "$\\\\epsilon^{\\\\text{older-adult}}_L$")
}
```

@@

```{r 10-overview-fig, fig.scap = "Observed and predicted TB incidence stratified by model age group", fig.cap = "Observed and predicted TB incidence stratified by model age group (0-11). 0-9 refers to 5 year age groups from 0-4 years old to 45-49 years old. 10 refers to those aged between 50 and 69 and 11 refers to those aged 70+. The model underpredicted incidence in all age groups fitted too with older adults have the best fit.", eval = FALSE}
knitr::include_graphics(file.path(plots_path, "overview-scenarios-2000-obs-1.png"))
```
